Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-11 paper/flairs27/content/system.tex
Minor fixes

We use Wikipedia API to automatically retrieve aliases. 
The API allows us to requests pages that redirect users to an entity page.
For example, if a WP user tries to access the \textsl{William Henry Gates} they are sent to the page for 
\textsl{Bill Gates} therefore we treat these two names as aliases. 
To extract more aliases  is we parse the HTML source of a WP entity page.
Then using regular expressions we extract the bold phrases of the initial paragraph as aliases.
Based on our observation this is a very accurate method and it provides several entities of 
WP entities \ceg{Do we know how many additional aliases this method provides?}.
\ceg{Do you want to give a more concrete example of how this might now work? It may be TMI.}
%As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.

@@

\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
%\includegraphics[width=6in]{./images/Pattern.eps}
%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
\includegraphics[width = 13cm]{./images/Pattern-crop.pdf}
% cropped pdf created using $ pdfcrop Pattern.pdf
\vspace*{-.1in}
\caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
entity. The pattern context discovered is `passed away' with a value of `March 2013'. }\label{fig:pattern}
\vspace*{-.2in}
\end{figure}

@@

\subsubsection{Constraints and Inference}\ceg{what specifically about the algorithm causes duplicates and errors?}

>>>>

We use Wikipedia API to automatically retrieve aliases. 
The API allows us to requests pages that redirect users to an entity page.
For example, if a WP user tries to access the \textsl{William Henry Gates} they are sent to the page for 
\textsl{Bill Gates} therefore we treat these two names as aliases. 
To extract more aliases  is we parse the HTML source of a WP entity page.
Then using regular expressions we extract the bold phrases of the initial paragraph as aliases.
Based on our observation this is a very accurate method and it provides several entities of 
WP with more inline aliases from the wiki page itself. As an example, for `Boris Berezovski' which was mentioned early-on, there is an alias of `Boris Abramovich Berezovsky' given in bold in the wiki page which will be obtained via thi method.

%\ceg{Do we know how many additional aliases this method provides?}.
%\ceg{Do you want to give a more concrete example of how this might now work? It may be TMI.}
%As an example of when this might not wirk, is that there might be occasions that some other topic is written in bold typesetting in the first paraph apart from the entity aliases itself but these are very rare.

@@

\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
%\includegraphics[width=6in]{./images/Pattern.eps}
%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
\includegraphics[width = 11cm]{./images/Pattern-crop.pdf}
% cropped pdf created using $ pdfcrop Pattern.pdf
\vspace*{-.1in}
\caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
entity. The pattern context discovered is `passed away' with a value of `March 2013'. }\label{fig:pattern}
\vspace*{-.2in}
\end{figure}

@@

\subsubsection{Constraints and Inference}\ceg{what specifically about the algorithm causes duplicates and errors? --- I asked Yang to elaborate on this as he is more familiar but still not sure what's causing those issues}
